HO unification from object language to meta language

### 2024-02-12 main.tex
update tex

\noindent In particular a \elpiIn{ml.uv} term is meant as a unification variable
of the meta-language. Therefore, the unification between \elpiIn{ml.lam x\
ml.lam y\ ml.uv 1 [x, y]} and \elpiIn{ml.lam x\ ml.lam y\ ml.uv 0 [x]} is
supposed to be unified by the internal unification procedure of the \ml (for
this example, the substitution for \elpiIn{uv 0} is \elpiIn{ml.lam x\ ml.lam y\
ml.uv 2 [x]} whereas the substitution for \elpiIn{uv 1} is \elpiIn{ml.lam x\
ml.uv 2 [x]}).

>>>>

\noindent In particular a \elpiIn{ml.uv} term is meant as a unification variable
of the meta-language. Therefore, the unification between

\begin{equation*}
  \texttt{\elpiIn{ml.lam x\ ml.lam y\ ml.uv 1 [x, y]}}
\end{equation*}

and

\begin{equation*}
  \texttt{\elpiIn{ml.lam x\ ml.lam y\ ml.uv 0 [x]}}
\end{equation*}

is supposed to procedure of the substitution \elpiIn{ml.lam x\ ml.lam y\ ml.uv 2
[x]} for \elpiIn{uv 0} and the substitution \elpiIn{ml.lam x\ ml.uv 2 [x]}) for
\elpiIn{uv 1}.
